---
title       : Slidify Presentation
subtitle    : Coursera's Developing Data Products
author      : Fturrado
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Slide 2: Welcome

In the next slides we will show some features of the slidify R package.

For all the examples we will use the iris dataset.

The main goal of this app is to classify new instances of data using a Random Forest Classifier trained over the original dataset.



--- .class #id 

## Slide 3: Data

The iris dataset contains 150 obervations of 5 features: Sepal.Width, Sepal.Length, Petal.Width, Petal.Length and Species. 

```{r,echo=FALSE}
summary(iris);
```

--- {tpl: twocol}

## Slide 4: Feature Overview

In this slide you will find an overview of the numeric features.

*** {name: left}

- Sepal.Width
- Sepal.Length
- Petal.Width
- Petal.Length

*** {name: right}

```{r,echo=FALSE}
par(mfrow=c(2,2))
hist(iris$Sepal.Width, col = 'blue', border = 'white')
hist(iris$Sepal.Length, col = 'blue', border = 'white')
hist(iris$Petal.Width, col = 'blue', border = 'white')
hist(iris$Petal.Length, col = 'blue', border = 'white')
```

--- 

## Slide 5 : Thanks

Please enjoy the app at the shinyapp's site:

https://fturrado.shinyapps.io/dataprod/




